---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# testyverse

<!-- badges: start -->
<!-- badges: end -->

The goal of testyverse is to ...

## Installation

You can install the released version of testyverse from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("testyverse")
```

# `testyverse` - an analysis and tutorial on the R software testing universe

TODO: testing is ace

TODO: don't be an evangelical arse about anything

TODO: Do most CRAN packages use a testing library?

TODO: For those that do, which one do they use?

TODO: And what of ancillary testing tools: hedgehog, covr, mutant, autotest, mockery, shinytest,
unitizer

TODO: Any package-package correlations between testing tools

## Testing packages

For unit testing there are several main tools available in R:

- testthat
- RUnit
- testit
- tinytest

TODO: similarities and differences between the packages

<!---
# Test syntax
# An example passing test
# An example failing test
# How do you structure your test files
# Can you run test files individually
# Integration of testing with R CMD check
# Integration of testing with RStudio
-->

### {testthat}

### {RUnit}

Features:
- Provides test-success and coverage report.

### {testit}

Features:
- Nope. It just tests your stuff.

Tests look like this:

```{r}
testit::assert("{testit} has the least to learn", {
  # All statements in parentheses should evaluate TRUE
  (TRUE)
  (123 > 0)
})
```

```{r, error = TRUE}
# Non-passing tests throw an error

testit::assert("{testit} tells you the least", {
  summer <- function(x, y) x + y
  (summer(1, 1) == 3)
})
```

<!--- That's quite a nice example of non-standard evaluation; consider for tidyeval course? -->

Test directory looks like this:

```
./tests
├── test-all.R
└── testit
    └── test-vectors.R
```

The test runner looks like this:

```
# ./tests/test-all.R
library(testit)
testit::test_pkg("myPackage")
```

Tests are automatically ran during `R CMD check` with no further changes.
No integration with `devtools::test()`

GPL3

### {tinytest}

Tests look very similar to {testthat} syntax (although you can use RUnit syntax in test files, we
won't cover that here).

```{r}
# {tinytest} uses `expect_*` syntax
# the functions are name::spaced to avoid confusion with the {testthat} equivalents

tinytest::expect_equal(
  current = 1 + 1,
  target = 2,
  info = "Maths still works"
)

tinytest::expect_equivalent(
  current = tibble::tibble(x = 1),
  target = data.frame(x = 1)
)

# Failing tests do not raise an error
tinytest::expect_true(FALSE)
```

The directory structure for {tinytest} tests looks like this:

```
./inst
└── tinytest
    └── test-vectors.R
./tests
└── tinytest.R
```

The test runner looks like this:

```
# ./tests/tinytest.R
if (requireNamespace("tinytest", quietly = TRUE)) {
  tinytest::test_package("myPackage")
}
```

NO! That can't be right.
In `R CMD check`, as ran from RStudio's Build panel, `./tests/tinytest.R` is ran, but a failing test
in `./inst/tinytest/test-vectors.R` does not lead to `R CMD check` failing.
This turned out to be due to using `tinytest::expect_equal` in a test script, rather than the
bare function name `expect_equal`.

Different results depending on how you express the tests:
```
# the results from this test won't be registered (so will be ignored by R CMD check)
tinytest::expect_equal(...)

# the results from this test will be registered (and test failures will be caught by R CMD check)
expect_equal(...)
```

Will this make it difficult to migrate from / to testthat?

<!-- If a file doesn't exist then run_test_file("not-a-file.R") returns without error / warning -->

Features:

- `tinytest::setup_tinytest("myPackage")`
  - adds ./tests/tinytest.R and ./inst/tinytest/test_<packageName>.R
- Monitoring of side-effects
- Test code is installed with your package
- No dependencies (beyond base R packages)

TODO:
- testing shiny
- assertyverse ({checkmate}, {assertthat}, {assertr}, {assertive})