---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# testyverse

<!-- badges: start -->
<!-- badges: end -->

The goal of testyverse is to ...

## Installation

You can install the released version of testyverse from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("testyverse")
```

# `testyverse` - an analysis and tutorial on the R software testing universe

TODO: testing is ace

TODO: don't be an evangelical arse about anything

TODO: Do most CRAN packages use a testing library?

TODO: For those that do, which one do they use?

TODO: And what of ancillary testing tools: hedgehog, covr, mutant, autotest, mockery, shinytest,
unitizer

TODO: Any package-package correlations between testing tools

## Testing packages

For unit testing there are several main tools available in R:

- testthat
- RUnit
- testit
- tinytest

TODO: similarities and differences between the packages

### {testthat}

### {RUnit}

Features:
- Provides test-success and coverage report.

### {testit}

Features:
- Nope. It just tests your stuff.

Tests look like this:

```{r}
testit::assert("testit has the least to learn", {
  # All statements in parentheses should evaluate TRUE
  (TRUE)
  (123 > 0)
})
```

```{r, error = TRUE}
testit::assert("testit tells you the least", {
  summer <- function(x, y) x + y
  (summer(1, 1) == 3)
})
```

<!--- That's quite a nice example of non-standard evaluation; consider for tidyeval course? -->

Test directory looks like this:

```
./tests
├── test-all.R
└── testit
    └── test-vectors.R
```

The test runner looks like this:

```
# ./tests/test-all.R
library(testit)
testit::test_pkg("myPackage")
```

Tests are automatically ran during `R CMD check` with no further changes.
No integration with `devtools::test()`

GPL3

### {tinytest}